Sampling requirements to detect ecosystem change

### 2020-06-29 R/manuscript_draft.Rmd
small spelling changes

Because ecological systems are dynamic in both space and time, it is essential that sampling designs account for spatio-temporal dynamics [@Williams2018]. To estimate a particular parameter, e.g. population abundance, optimal spatial sampling strategies are based on spatially balanced sampling [@Kermorvant2019], while optimal temporal sampling strategies are more cost efficient with a targeted sampling, e.g., around the period of reproduction [@Jackson2008a]. In either case, sampling time and lcoations can be chosen in an iterative process to be cost-effective and reduce the uncertainty in the process [@Hooten2009]. With the ability to choose precisely when to sample, we can move beyond random, interval, or opportunistic sampling designs. This is particuraly relevant in situations where a subset of samples already collected need to be analyzed.

>>>>

Because ecological systems are dynamic in both space and time, it is essential that sampling designs account for spatio-temporal dynamics [@Williams2018]. To estimate a particular parameter, e.g. population abundance, optimal spatial sampling strategies are based on spatially balanced sampling [@Kermorvant2019], while optimal temporal sampling strategies are more cost efficient with a targeted sampling, e.g., around the period of reproduction [@Jackson2008a]. In either case, sampling time and locations can be chosen in an iterative process to be cost-effective and reduce the uncertainty in the process [@Hooten2009]. With the ability to choose precisely when to sample, we can move beyond random, interval, or opportunistic sampling designs. This is particularly relevant in situations where a subset of samples already collected need to be analyzed.
